MNRAS \LaTeXe\ template -- title goes here

### 2017-08-18 Paper/mnras_template.tex
Some advances
Small improvement of illustris section

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content. This was achieved by following the evolution of $1820^3$ DM particles with mass resolution $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$, together with $1820^3$ baryonic particles with mass resolution $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration, in a periodic box of $106.5\text{Mpc}$, all of which is consistent with a standard $\Lambda \text{CDM}$ cosmology with $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$. Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation. \\

The evolution in time was performed with the hydrodynamic algorithm AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach. Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs. The level of detail in Illustris is advantageous and hard to find among other simulations, and is the reason why we chose it to perform our calculations.\\

This simulation consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed with modified versions of FOF and SUBFIND algorithms \cite{fof,subfind} to generate halo and subhalo catalogues with their respective characterization properties.

@@

\subsection{The cosmic web method}
To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al.. The method chosen here was

>>>>

\section{Illustris Simulation}
Illustris-1, also known simply as Illustris, is a highly resolved cosmological simulation which reproduces large-scale statistical features of the Universe, such as the galaxy population of massive clusters, as well as small-scale properties such as the morphology of galaxies and detailed values for their stellar and gas content.\\

This was achieved by following the evolution of $2 \times 1820^3$ elements with dark mass resolution of $m_{\text{DM}} = 6.26\cdot 10^6\text{M}_{\odot}$ and initial baryonic mass resolution of $\overline{\text{m}_\text{b}}=1.26\cdot 10^6\text{M}_{\odot}$ from a glass-like configuration in a periodic box of $106.5\text{Mpc}$. The $\Lambda \text{CDM}$ cosmology of this run follows: $\Omega_\Lambda=0.7274$, $\Omega_\text{m}=0.2726$, $\Omega_\text{b}=0.0456$, $\sigma_\text{s}=0.0809$, $\text{n}_\text{s}=0.963$ \& $\text{H}_0=70.4\text{kms}
^{-1}\text{Mpc}^{-1}$ which is consistent with the (last) Anisotropy Probe (WMAP)-9 \cite{AnisotropyProbe}. Illustris has a constant spatial resolution of $1.4\text{kpc}$ for DM particles in comoving units, and for baryonic particles it has the same spatial resolution of DM for $\text{z}\geq 1$, which is later modified to $0.7\text{kpc}$ in physical units for the rest of the simulation. \\

The evolution in time was performed with the hydrodynamic code AREPO \cite{arepo}, which combines a moving Voronoi tessellation with the finite volume approach. Included in the evolution algorithm, there are galaxy formation models which account for the evolution of stars and SMBHs. Specifically, the physics followed by this model includes energetic feedback from supermassive black holes and supernovae, as well as stellar evolution and chemical enrichment. This level of detail in Illustris is advantageous for the analysis of the effect of the environment  in galactic barionic properties and is hard to find among other simulations, i.e. post-processed runs with semi-analytical models which do not directly simulate baryons.(Expand) Describe Arepo a little bit more\\

The output of this simultaion consists of 136 snapshots where 61 of them were taken at $z < 3$ spaced with a cosmological scale factor $\Delta a \approx 0.02$, while the remaining 75 were taken at $z > 3$ with spacing $\Delta a \approx 0.01$. Each snapshot was post-processed with a modified version of FOF \cite{FOF} to identify DM haloes with more than 32 particles using a linking length of 0.2 times the mean particle separation each of which is analyzed with the SUBFIND algorithm \cite{subfind} to generate, at z=0, 7,713,601 halos (FOF) and 4,366,546 (sub)halo catalogues with their respective characterization properties. \\

(HERE TALK ABOUT ILLUSTRIS-2,3 FOR RESOLUTION PURPOSES)

@@

\subsection{The cosmic web method}
To complement the analysis performed with the third nearest neighbor method for the classification of environments, we chose a complementary method of completely different nature to verify even more the results from Jones et al.. The method chosen here was the one developed by Forero et al. \cite{forero1}, which uses the Hessian of the gravitational potential obtained from the DM field to classify galaxies into (conveniently) four morphological environments.\\
